Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-10-08 grove-paper.tex
Get macros setup for vertex and edge names (Michael D. Adams)

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
TODO
\caption{User interface}
\label{fig:A simple tree with a hole-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"'],
   {}
  }
 }
};
\end{tikzpicture}
\caption{Graph representation}
\label{fig:A simple tree with a hole-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole}
\label{fig:A simple tree with a hole}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
TODO
\caption{User interface}
\label{fig:Construction-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"'],
   "$\texttt{y}_{6}$" [> "R$_{5}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:A simple tree with a hole-b} after adding \Vertex{6} and \Edge{5}}
\label{fig:Construction-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction}
\label{fig:Construction}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"'],
   {}
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 y [as={$\texttt{y}_{6}$}]
};
\end{tikzpicture}
\caption{\autoref{fig:Construction-b} after deleting \Edge{5}}
\label{fig:Change-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}[framed]
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{*}_{2}$" [> "Root$_{1}$"] -> {
   "$\texttt{x}_{4}$" [> "L$_{3}$"'],
   "$\texttt{z}_{8}$" [> "R$_{7}$"]
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 "$\texttt{y}_{6}$"
};
\end{tikzpicture}
\caption{\autoref{fig:Change-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Change-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Change}
\label{fig:Change}
\end{figure}

@@

\begin{figure}
% TODO: naive add that creates a conflict
% \begin{tikzpicture}
% \path (0,0)       node {\includegraphics[scale=0.4]{graphviz/wrapping/1.dot}};
% \path (0cm,-4cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/2.dot}};
% \path (0cm,-8cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/3.dot}};
% \path (0cm,-12cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/4.dot}};
% \path (0cm,-16cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/5.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (-0.5,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{3}$"'],
  "$\texttt{z}_{8}$" [> "R$_{7}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Change-b} after deleting \Edge{1}}
\label{fig:Wrapping-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"]
 }
};
\path (-0.5cm,-3cm) graph[graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{5}$"'],
  "$\texttt{z}_{8}$" [> "R$_{7}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Wrapping-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{11}$"'] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{z}_{8}$" [> "R$_{7}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-b} after adding \Edge{9}}
\label{fig:Wrapping-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure}

@@

\begin{figure}
% \centering
% \begin{tikzpicture}
% \path (0,0)    node {\includegraphics[scale=0.75]{graphviz/move/1.dot}};
% \path (0,-5cm) node {\includegraphics[scale=0.75]{graphviz/move/2.dot}};
% \path (0,-9cm) node {\includegraphics[scale=0.75]{graphviz/move/3.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"]
 }
};
\path (0cm,-3cm) graph [graph style] {
 "$\texttt{*}_{2}$" -> {
  "$\texttt{x}_{4}$" [> "L$_{3}$"'],
  "$\texttt{z}_{8}$" [> "R$_{7}$"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-c} after deleting \Edge{9}}
\label{fig:Move-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.45\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{z}_{6}$" [> "R$_{7}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-a} after adding \Edge{11}}
\label{fig:Move-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \Vertex{2} from the left child to the right child of \Vertex{8}}
\label{fig:Move}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{z}_{6}$" [> "R$_{7}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{x}_{4}$" [> "L$_{3}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{2}$" [> "R$_{13}$"] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{24}$" [> "R$_{23}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   "$\texttt{y}_{26}$" [> "R$_{25}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{24}$" [> "R$_{23}$"],
    "$\texttt{y}_{26}$" [> "R$_{25}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

>>>>

% Calling \newvertex{Foo}{bar} defines
%   \vidFoo to be a new id number, and
%   \vFoo to be \texttt{bar}\ensuremath{_{\vidFoo}}
\newcounter{NodeVertexCounter}
\newcommand{\newvertex}[2]{%
\ifodd\theNodeVertexCounter
  \addtocounter{NodeVertexCounter}{1}%
\else
  \addtocounter{NodeVertexCounter}{2}%
\fi
\expandafter\newcommand\csname vid#1\endcsname{}% This is just to check if this is a redefinition
\expandafter\global\expandafter\edef\csname vid#1\endcsname{\theNodeVertexCounter}%
\expandafter\newcommand\csname v#1\endcsname{}% This is just to check if this is a redefinition
\expandafter\gdef\csname v#1\endcsname{\texttt{#2}\ensuremath{_{\csname vid#1\endcsname}}}%
}
\newcommand{\newedge}[2]{%
\ifodd\theNodeVertexCounter
  \addtocounter{NodeVertexCounter}{2}%
\else
  \addtocounter{NodeVertexCounter}{1}%
\fi
\expandafter\newcommand\csname eid#1\endcsname{}% This is just to check if this is a redefinition
\expandafter\global\expandafter\edef\csname eid#1\endcsname{\theNodeVertexCounter}%
\expandafter\newcommand\csname e#1\endcsname{}% This is just to check if this is a redefinition
\expandafter\gdef\csname e#1\endcsname{\texttt{#2}\ensuremath{_{\csname eid#1\endcsname}}}%
}
\setcounter{NodeVertexCounter}{-1}
\newvertex{Root}{Root}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
TODO
\caption{User interface}
\label{fig:A simple tree with a hole-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\end{tikzpicture}
TODO: labels for edge numbers

TODO: sub figure with diagram of relation of subfigures

TODO: move subcaptions into master caption

TODO: move subcaptions above figure

TODO: top align subfigures
\caption{Graph representation}
\label{fig:A simple tree with a hole-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{A simple tree with a hole}
\label{fig:A simple tree with a hole}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
TODO
\caption{User interface}
\label{fig:Construction-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\columnwidth}
\centering
\newedge{ConstructionY}{R}%
\newvertex{ConstructionY}{y}%
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vConstructionY" [> "\eConstructionY"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:A simple tree with a hole-b} after adding \Vertex{6} and \Edge{5}}
\label{fig:Construction-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Construction}
\label{fig:Construction}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   {}
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 y [as={$\texttt{y}_{6}$}]
};
\end{tikzpicture}
\caption{\autoref{fig:Construction-b} after deleting \Edge{5}}
\label{fig:Change-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\newedge{ChangeZ}{R}
\newvertex{ChangeZ}{z}
\begin{tikzpicture}[framed]
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vSimpleTimes" [> "\eSimpleTimes"] -> {
   "\vSimpleX" [> "\eSimpleX"'],
   "\vChangeZ" [> "\eChangeZ"]
  }
 }
};
\path (1cm,-2cm) graph[graph style] {
 "$\texttt{y}_{6}$"
};
\end{tikzpicture}
\caption{\autoref{fig:Change-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Change-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Change}
\label{fig:Change}
\end{figure}

@@

\begin{figure}
% TODO: naive add that creates a conflict
% \begin{tikzpicture}
% \path (0,0)       node {\includegraphics[scale=0.4]{graphviz/wrapping/1.dot}};
% \path (0cm,-4cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/2.dot}};
% \path (0cm,-8cm)  node {\includegraphics[scale=0.4]{graphviz/wrapping/3.dot}};
% \path (0cm,-12cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/4.dot}};
% \path (0cm,-16cm) node {\includegraphics[scale=0.4]{graphviz/wrapping/5.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style]
};
\path (-0.5,-3cm) graph[graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Change-b} after deleting \Edge{1}}
\label{fig:Wrapping-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{WrapPlus}{Root}
\newvertex{WrapPlus}{+}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-0.5cm,-3cm) graph[graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-a} after adding \Vertex{8} and \Edge{7}}
\label{fig:Wrapping-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\newedge{WrapTimes}{L}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eWrapTimes"'] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "\vChangeZ" [> "\eChangeZ"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-b} after adding \Edge{9}}
\label{fig:Wrapping-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure}

@@

\begin{figure}
% \centering
% \begin{tikzpicture}
% \path (0,0)    node {\includegraphics[scale=0.75]{graphviz/move/1.dot}};
% \path (0,-5cm) node {\includegraphics[scale=0.75]{graphviz/move/2.dot}};
% \path (0,-9cm) node {\includegraphics[scale=0.75]{graphviz/move/3.dot}};
% \end{tikzpicture}
\hfill
%%%%%%%%
\begin{subfigure}{0.49\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (0cm,-3cm) graph [graph style] {
 "\vSimpleTimes" -> {
  "\vSimpleX" [> "\eSimpleX"'],
  "\vChangeZ" [> "\eChangeZ"]
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Wrapping-c} after deleting \Edge{9}}
\label{fig:Move-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.45\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "R$_{13}$"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "$\texttt{z}_{6}$" [> "\eChangeZ"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-a} after adding \Edge{11}}
\label{fig:Move-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Moving \Vertex{2} from the left child to the right child of \Vertex{8}}
\label{fig:Move}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "R$_{13}$"] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{z}_{6}$" [> "\eChangeZ"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Alice replaces \Vertex{4} with \Vertex{12}}
\label{fig:Editing Different Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "R$_{13}$"] -> {
    "\vSimpleX" [> "\eSimpleX"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Move-b} after Bob replaces \Vertex{6} with \Vertex{14}}
\label{fig:Editing Different Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "R$_{13}$"] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Different Parts of the Code-a} with \autoref{fig:Editing Different Parts of the Code-b}}
\label{fig:Editing Different Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Different Parts of the Code}
\label{fig:Editing Different Parts of the Code}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vSimpleTimes" [> "R$_{13}$"] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice replaces \Vertex{14} with \Vertex{16}}
\label{fig:Editing Nested Parts of the Code-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{u}_{16}$" [> "L$_{15}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob move \Vertex{2} to the left child of \Vertex{8}}
\label{fig:Editing Nested Parts of the Code-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Editing Nested Parts of the Code-a} with \autoref{fig:Editing Nested Parts of the Code-b}}
\label{fig:Editing Nested Parts of the Code-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Editing Nested Parts of the Code}
\label{fig:Editing Nested Parts of the Code}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{24}$" [> "R$_{23}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   "$\texttt{y}_{26}$" [> "R$_{25}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{24}$" [> "R$_{23}$"],
    "$\texttt{y}_{26}$" [> "R$_{25}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}
